---
title: "UFO_Meteorite_PRJ"
author: "Felix G., Will R."
format: html
embed-resources: true
---

```{r}
# Load libraries
library(tidyverse)
library(sf)
library(mapview)
```


## Starting off

### Importing files

```{r}
# Load in files

ufoData <- read.csv("Data/ufo_sightings.csv")

metData <- read.csv("Data/Meteorite_Landings.csv")

head(ufoData)
head(metData)
```

### Data wrangling

After reviewing the available information in these data sets, we decided to make
our target DataFrame the following:
`Year, Lat, Long, Type`

* `Year` = the year of the meteorite or UFO sighting
* `Lat` = the latitude of the event
* `Long` = the longitude of the event
* `Type` = the type of the event (Meteorite or UFO sighting)

We will be analyzing whether there is a correlation between the location of the 
event and the year in which they happened.

```{r}
# Tidy up data for usability
# 1) Select from UFO data set for associated columns
# 2) Select from Meteorite data set for associated columns
# 3) Combine data into single tibble
# This can be done as a "single" operation using pipes

ufoFrame <- ufoData |>
  select(
    Dates.Sighted.Year,
    Location.Coordinates.Latitude.,
    Location.Coordinates.Longitude.
  ) |>
  mutate(type = "UFO") |>
  arrange(Dates.Sighted.Year)

ufoFrame
```

### Data exploration

```{r}
# Look for correlations
mapview(ufoFrame, xcol = "Location.Coordinates.Longitude.", ycol = "Location.Coordinates.Latitude.", crs = 4269)
```



